plottingScript

### 2023-05-18 analyses/plotter.Rmd
StatSubmission

  if(method=="C-Index"){
    method=expression("C"["IPCW"])
  }   
  metricSummary#<- metricSummary[-which(metricSummary$model=="CBNN_Spline"),]
  #mainTitle<-paste(method,' : 95% P.I. over ', iterations, ' iterations',sep='')
  colnames(metricSummary)[1]<-"Models"
  a<-ggplot(data=metricSummary, aes(x=times,y=means,col=Models))+
    geom_line() +
    geom_ribbon(aes(ymin=cilower95,ymax=ciupper95,fill=Models),linetype=0,alpha=0.3) +
    ggtitle(mainTitle) + 
    xlab(xlab) +
    ylab(method)+
    theme_minimal()+
    scale_color_manual(values=unique(metricSummary$color))+
    scale_fill_manual(values=unique(metricSummary$color))+
    scale_x_continuous(n.breaks=6)
  # scale_color_manual(labels = metricSummary$model, values = metricSummary$color)

@@

```{r megaplot,fig.height=12,fig.width=12}
#complex[[4]]$layers[[2]]<-NULL
pt <- plot_grid(
  complex[[1]]+ theme(legend.position="none")+ ggtitle("Complex simulation")+ labs(x = "")+coord_cartesian(ylim=c(-0.3,0.7)),
  myeloma[[1]]+ theme(legend.position="none")+ ggtitle("MM")+ labs(x = "",y="")+coord_cartesian(ylim=c(-1,.1)),
  flchain[[1]]+ theme(legend.position="none")+ ggtitle("FLC")+ labs(x = "",y="")+coord_cartesian(ylim=c(-0.025,.45)),
  prostate[[1]]+ theme(legend.position="none")+ ggtitle("Prostate")+ labs(x = "",y="")+coord_cartesian(ylim=c(-0.02,0.205)),
  complex[[5]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)")+coord_cartesian(ylim=c(0.68,1)),
  myeloma[[5]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.00,0.75)),
  flchain[[5]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.8,0.875)),
  prostate[[5]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.65,0.82)),
  # complex[[4]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)")+coord_cartesian(ylim=c(0.5,0.8)),
  # myeloma[[4]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.4,0.65)),
  # flchain[[4]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.65,0.9)),
  # prostate[[4]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.5,0.73)),
  labels = c('A',"B","C","D",'E','F','G',"H"),#,"I","J","K","L"),
  ncol=4)
legend <- get_legend(
  # create some space to the left of the legend
  complex$ipa  +
    guides(color = guide_legend(nrow = 2)) +
    theme(legend.position = "bottom")+
    theme(legend.text=element_text(size=8))
)

g<-plot_grid(pt, legend,ncol = 1, rel_heights = c(1, .1), rel_widths = c(3, .4))
pdf(file="../StatPaper/figures/Figure2.pdf",width=16,height=9)
g
dev.off()
```

@@

  ft <- add_header_row(x = ft, values = c(title,"IPA","AUC"),
                       colwidths = c(1,4,4))
  # ft <- compose(ft, part = "header", i = 1, j = 6,
  #               value = as_paragraph("C",
  #                                    as_sub("IPCW")))
  #ft<-bold(ft, bold = TRUE, part = "header")

>>>>

  if(method=="C-Index"){
    method=expression("C"["IPCW"])
  }   
  #   if(method=="AUC"){
  #   method=expression("C"["IPCW"])
  # }   
  metricSummary#<- metricSummary[-which(metricSummary$model=="CBNN_Spline"),]
  #mainTitle<-paste(method,' : 95% P.I. over ', iterations, ' iterations',sep='')
  colnames(metricSummary)[1]<-"Models"
  a<-ggplot(data=metricSummary, aes(x=times,y=means,col=Models))+
    geom_line() +
    geom_ribbon(aes(ymin=cilower95,ymax=ciupper95,fill=Models),linetype=0,alpha=0.3) +
    ggtitle(mainTitle) + 
    xlab(xlab) +
    ylab(method)+
    theme_minimal()+
    scale_color_manual(values=unique(metricSummary$color))+
    scale_fill_manual(values=unique(metricSummary$color))+
    scale_x_continuous(n.breaks=6)
  # scale_color_manual(labels = metricSummary$model, values = metricSummary$color)

@@

```{r megaplot,fig.height=12,fig.width=12}
#complex[[4]]$layers[[2]]<-NULL

sz<-18
szx<-15
pt <- plot_grid( 
  complex[[1]]+ theme(legend.position="none")+ ggtitle("Complex simulation")+ labs(x = "")+coord_cartesian(ylim=c(-0.3,0.7))+theme(plot.title = element_text(size=sz)) +theme(axis.title.y=element_text(size=sz))+theme(axis.text=element_text(size=szx)),
  myeloma[[1]]+ theme(legend.position="none")+ ggtitle("MM")+ labs(x = "",y="")+coord_cartesian(ylim=c(-1,.1)) + theme(plot.title = element_text(size=sz))+theme(axis.text=element_text(size=szx)),
  flchain[[1]]+ theme(legend.position="none")+ ggtitle("FLC")+ labs(x = "",y="")+coord_cartesian(ylim=c(-0.025,.45)) + theme(plot.title = element_text(size=sz))+theme(axis.text=element_text(size=szx)),
  prostate[[1]]+ theme(legend.position="none")+ ggtitle("Prostate")+ labs(x = "",y="")+coord_cartesian(ylim=c(-0.02,0.205)) + theme(plot.title = element_text(size=sz))+theme(axis.text=element_text(size=szx)),
  complex[[5]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y=expression("AUC"["IPCW"]))+coord_cartesian(ylim=c(0.68,1)) +theme(axis.title.y=element_text(size=sz),axis.title.x=element_text(size=sz))+theme(axis.text=element_text(size=szx)),
  myeloma[[5]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.00,0.75)) +theme(axis.title.x=element_text(size=sz))+theme(axis.text=element_text(size=szx)),
  flchain[[5]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.8,0.875)) +theme(axis.title.x=element_text(size=sz))+theme(axis.text=element_text(size=szx)),
  prostate[[5]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.65,0.82)) +theme(axis.title.x=element_text(size=sz))+theme(axis.text=element_text(size=szx)),
  # complex[[4]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)")+coord_cartesian(ylim=c(0.5,0.8)),
  # myeloma[[4]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.4,0.65)),
  # flchain[[4]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.65,0.9)),
  # prostate[[4]]+ theme(legend.position="none")+ labs(x = "Follow-up time (years)",y="")+coord_cartesian(ylim=c(0.5,0.73)),
  labels = c('A',"B","C","D",'E','F','G',"H"),#,"I","J","K","L"),
  ncol=4)
legend <- get_legend(
  # create some space to the left of the legend
  complex$ipa  +
    guides(color = guide_legend(nrow = 2)) +
    theme(legend.position = "bottom")+
    theme(legend.text=element_text(size=sz))
)

g<-plot_grid(pt, legend,ncol = 1, rel_heights = c(1, .1), rel_widths = c(3, .4))
pdf(file="../StatPaper/figures/Figure2.pdf",width=18,height=10)
g
dev.off()
```

@@

  ft <- add_header_row(x = ft, values = c(title,"IPA", "AUC" ),
                       colwidths = c(1,4,4))
   ft <- compose(ft, part = "header", i = 1, j = 6,
                 value = as_paragraph("AUC",
                                      as_sub("IPCW")))
  #ft<-bold(ft, bold = TRUE, part = "header")
